---
title: "NLP Tutorial 01: Preprocessing"
author: "Ben Ortiz"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
description: "The purpose of this book is to provide R code supplementing the NLP tutorial covering *preprocessing*."
output:
  bookdown::gitbook: default
---

# Intro

*The purpose of this book is to provide R code supplementing the NLP tutorial covering *preprocessing*

## Prerequisites 

The following packages are necessary to follow the material in this book.

```{r, eval=F}
install.packages(c(
  'dplyr', #utilities for data cleaning
  'fastNaiveBayes', #NB implementation
  'gmodels', #display results of model
  'magrittr', #allow piping
  'Matrix', #create sparse matrices
  'MLmetrics', #get F1 score
  'readr', #read in data
  'stringr', #utilities for string manipulation
  'tidytext', #TIDY version of text mining
  'tm' #text mining
))
```

## Package usage

We will explicitly refer to packages when we use a function. This takes the form of `package::function()`. The reason we do this is to be clear where functions are coming from.

The only exception to this is **magrittr**'s `%>%` (pipe) function. This is to allow some of our code to be more legible  

```{r}
library(magrittr)
```

If you haven't used `%>% before, then think of it as using the output of a previous function as the input of the next function.

That is rather than nesting functions:

```{r}
sqrt(sum(log(c(1, 10, 100))))
```

We can focus on functions in the order they are called

```{r}
c(1,10,100) %>%
  log() %>%
  sum() %>%
  sqrt()
```
