---
title: "Network Analysis in R"
author: "Christian Conroy"
date: "September 15, 2019"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
require(knitr)
require(readxl)
require(ggplot2)

opts_chunk$set(echo = TRUE)
options(digits = 3)

opts_knit$set(root.dir ="~/GeorgetownMPPMSFS/McCourtMPP/RFiles/NLP Training for Acc")
```


# Module 1: Network Analysis with R and igraph: NetSci X Tutorial 
## https://kateto.net/networks-r-igraph



```{r message = FALSE}
library(igraph)
```

The code below generates an undirected graph with three edges. The numbers are interpreted as vertex IDs, so the edges are 1–>2, 2–>3, 3–>1.

```{r message = FALSE}
g1 <- graph( edges=c(1,2, 2,3, 3, 1), n=3, directed=F ) 

plot(g1) # A simple plot of the network - we'll talk more about plots later
class(g1)
g1
```

```{r message = FALSE, warning = FALSE}
# Now with 10 vertices, and directed by default:

g2 <- graph( edges=c(1,2, 2,3, 3, 1), n=10 )

plot(g2)  
g2

```

```{r message = FALSE, warning = FALSE}
g3 <- graph( c("John", "Jim", "Jim", "Jill", "Jill", "John")) # named vertices

# When the edge list has vertex names, the number of nodes is not needed

plot(g3)

# So think, it's all PAIRWISE!

g3

```


```{r message = FALSE, warning= FALSE}
g4 <- graph( c("John", "Jim", "Jim", "Jack", "Jim", "Jack", "John", "John"), 

             isolates=c("Jesse", "Janis", "Jennifer", "Justin") )  

# In named graphs we can specify isolates by providing a list of their names.

# Even though Jim, jack is listed twice, taking out one flips that part of the graph

plot(g4, edge.arrow.size=.5, vertex.color="gold", vertex.size=15, 

     vertex.frame.color="gray", vertex.label.color="black", 

     vertex.label.cex=0.8, vertex.label.dist=2, edge.curved=0.2)

```

Small graphs can also be generated with a description of this kind: - for undirected tie, +- or -+ for directed ties pointing left & right, ++ for a symmetric tie, and “:” for sets of vertices.

```{r message = FALSE}
plot(graph_from_literal(a---b, b---c)) # the number of dashes doesn't matter

```

```{r message = FALSE, warning= FALSE}
plot(graph_from_literal(a--+b, b+--c))

```


```{r message = FALSE, warning= FALSE}

plot(graph_from_literal(a+-+b, b+-+c)) 

```


```{r message = FALSE, warning= FALSE}

plot(graph_from_literal(a:b:c---c:d:e))

# So this is saying a and b and c are a set of vertices and are connected to c and d an e, another set of vertics 

```

```{r message = FALSE, warning= FALSE}

gl <- graph_from_literal(a-b-c-d-e-f, a-g-h-b, h-e:f:i, j)

plot(gl)

```
Edge, vertex, and network attributes

```{r message = FALSE, warning= FALSE}

E(g4) # The edges of the object (Most useful)

```


```{r message = FALSE, warning= FALSE}
V(g4) # The vertices of the object
```


```{r message = FALSE, warning= FALSE}
g4[]
```


```{r message = FALSE, warning= FALSE}
     
g4[1,] 
# Connections for John 

```

Figure 2.4 lets us spot an anomaly in the sentiment analysis; the word “miss” is coded as negative but it is used as a title for young, unmarried women in Jane Austen’s works. If it were appropriate for our purposes, we could easily add “miss” to a custom stop-words list using bind_rows(). We could implement that with a strategy such as this.

```{r message = FALSE, warning= FALSE}
V(g4)$name # automatically generated when we created the network.

```


```{r message = FALSE, warning= FALSE}
V(g4)$gender <- c("male", "male", "male", "male", "female", "female", "male")

E(g4)$type <- "email" # Edge attribute, assign "email" to all edges

E(g4)$weight <- 10    # Edge weight, setting all existing edges to 10))

# So we can give attriubtes to the nodes this way. 

```


```{r message = FALSE, warning= FALSE}

edge_attr(g4)

```

```{r message = FALSE, warning= FALSE}

vertex_attr(g4)

```


```{r message = FALSE, warning= FALSE}

graph_attr(g4)

```

Another way to set attributes (you can similarly use set_edge_attr(), set_vertex_attr(), etc.):

```{r message = FALSE, warning= FALSE}

g4 <- set_graph_attr(g4, "name", "Email Network")

g4 <- set_graph_attr(g4, "something", "A thing")

graph_attr_names(g4)

```


```{r message = FALSE, warning= FALSE}
graph_attr(g4, "name")
```

```{r message = FALSE, warning= FALSE}

g4 <- delete_graph_attr(g4, "something")

graph_attr(g4)
```



```{r message = FALSE, warning= FALSE}

plot(g4, edge.arrow.size=.5, vertex.label.color="black", vertex.label.dist=1.5,

     vertex.color=c( "pink", "skyblue")[1+(V(g4)$gender=="male")] ) 

```

The graph g4 has two edges going from Jim to Jack, and a loop from John to himself. We can simplify our graph to remove loops & multiple edges between the same nodes. Use edge.attr.comb to indicate how edge attributes are to be combined - possible options include sum, mean, prod (product), min, max, first/last (selects the first/last edge’s attribute). Option “ignore” says the attribute should be disregarded and dropped.

```{r message = FALSE, warning= FALSE}

g4s <- simplify( g4, remove.multiple = T, remove.loops = F, 

                 edge.attr.comb=c(weight="sum", type="ignore") )

plot(g4s, vertex.label.dist=1.5)

```


```{r message = FALSE, warning= FALSE}

g4s

```

The description of an igraph object starts with up to four letters:

D or U, for a directed or undirected graph
N for a named graph (where nodes have a name attribute)
W for a weighted graph (where edges have a weight attribute)
B for a bipartite (two-mode) graph (where nodes have a type attribute)
The two numbers that follow (7 5) refer to the number of nodes and edges in the graph. The description also lists node & edge attributes, for example:

(g/c) - graph-level character attribute
(v/c) - vertex-level character attribute
(e/n) - edge-level numeric attribute

2.3 Specific graphs and graph models

Empty Graph

```{r message = FALSE, warning= FALSE}

eg <- make_empty_graph(40)

plot(eg, vertex.size=10, vertex.label=NA)
eg

# So this one is just D for Directed (Even though only Vs)

```

Full graph

```{r message = FALSE, warning= FALSE}

fg <- make_full_graph(40)

plot(fg, vertex.size=10, vertex.label=NA)

# So full graph is everything connected to everything

```

Simple star graph

```{r message = FALSE, warning= FALSE}

st <- make_star(40)

plot(st, vertex.size=10, vertex.label=NA) 

```


Tree graph
```{r message = FALSE, warning= FALSE}

tr <- make_tree(40, children = 3, mode = "undirected")

plot(tr, vertex.size=10, vertex.label=NA) 

```

Ring Graph

```{r message = FALSE, warning= FALSE}

rn <- make_ring(40)

plot(rn, vertex.size=10, vertex.label=NA)

# Looks slightly different each timme. 

```

Erdos-Renyi random graph model
(‘n’ is number of nodes, ‘m’ is the number of edges).

```{r message = FALSE, warning= FALSE}
er <- sample_gnm(n=100, m=40) 

plot(er, vertex.size=6, vertex.label=NA) 

```


Watts-Strogatz small-world model

Creates a lattice (with dim dimensions and size nodes across dimension) and rewires edges randomly with probability p. The neighborhood in which edges are connected is nei. You can allow loops and multiple edges.


```{r message = FALSE, warning= FALSE}
sw <- sample_smallworld(dim=2, size=10, nei=1, p=0.1)

plot(sw, vertex.size=6, vertex.label=NA, layout=layout_in_circle)

```

Barabasi-Albert preferential attachment model for scale-free graphs
(n is number of nodes, power is the power of attachment (1 is linear); m is the number of edges added on each time step)

```{r message = FALSE, warning= FALSE}

 ba <-  sample_pa(n=100, power=1, m=1,  directed=F)

 plot(ba, vertex.size=6, vertex.label=NA)

```

Rewiring a graph

each_edge() is a rewiring method that changes the edge endpoints uniformly randomly with a probability prob

```{r message = FALSE, warning= FALSE}

 rn.rewired <- rewire(rn, each_edge(prob=0.1)) # rn is the ring graph we made earlier

 plot(rn.rewired, vertex.size=10, vertex.label=NA)

```

Rewire to connect vertices to other vertices at a certain distance.

```{r message = FALSE, warning= FALSE}

 rn.neigh = connect.neighborhood(rn, 5)

 plot(rn.neigh, vertex.size=8, vertex.label=NA) 
 
```

Combine graphs (disjoint union, assuming separate vertex sets): %du%



```{r message = FALSE, warning= FALSE}
 plot(rn, vertex.size=10, vertex.label=NA) 
```

```{r message = FALSE, warning= FALSE}
 plot(tr, vertex.size=10, vertex.label=NA) 
```

```{r message = FALSE, warning= FALSE}
plot(rn %du% tr, vertex.size=10, vertex.label=NA) 

# Very useful!
```

3. Reading network data from files

In the following sections of the tutorial, we will work primarily with two small example data sets. Both contain data about media organizations. One involves a network of hyperlinks and mentions among news sources. The second is a network of links between media venues and consumers. While the example data used here is small, many of the ideas behind the analyses and visualizations we will generate apply to medium and large-scale networks.

3.1 DATASET 1: edgelist
The first data set we are going to work with consists of two files, “Media-Example-NODES.csv” and “Media-Example-

```{r message = FALSE, warning= FALSE}
# Different media companies each with a unique id and attributes of media type and audience size
nodes <- read.csv("Dataset1-Media-Example-NODES.csv", header=T, as.is=T)

# From, To, weight, and type (hyperlink, mention)
links <- read.csv("Dataset1-Media-Example-EDGES.csv", header=T, as.is=T)
```

Examine the data 

```{r message = FALSE, warning= FALSE}

head(nodes)

head(links)

nrow(nodes); length(unique(nodes$id))

nrow(links); nrow(unique(links[,c("from", "to")]))

```

Notice that there are more links than unique from-to combinations. That means we have cases in the data where there are multiple links between the same two nodes. (So hyperlink and mention)

We will collapse all links of the same type between the same two nodes by summing their weights, using aggregate() by “from”, “to”, & “type”. We don’t use simplify() here so as not to collapse different link types.

```{r message = FALSE, warning= FALSE}
links <- aggregate(links[,3], links[,-3], sum)

links <- links[order(links$from, links$to),]

colnames(links)[4] <- "weight"

rownames(links) <- NULL

```

3.2 DATASET 2: matrix
Two-mode or bipartite graphs have two different types of actors and links that go across, but not within each type. Our second media example is a network of that kind, examining links between news sources and their consumers.

```{r message = FALSE, warning= FALSE}

# Just one group of actors on top of another
nodes2 <- read.csv("Dataset2-Media-User-Example-NODES.csv", header=T, as.is=T)

# A matrix of 0s and 1s signify connections or not between one type of actor and another
links2 <- read.csv("Dataset2-Media-User-Example-EDGES.csv", header=T, row.names=1)

```

Examine the data 
```{r message = FALSE, warning= FALSE}
head(nodes2)

head(links2)

```
We can see that links2 is an adjacency matrix for a two-mode network:



```{r message = FALSE, warning= FALSE}

links2 <- as.matrix(links2)

dim(links2)

dim(nodes2)

```

Turning Networks into igraph objects

We start by converting the raw data to an igraph network object. Here we use igraph’s graph.data.frame function, which takes two data frames: d and vertices.

d describes the edges of the network. Its first two columns are the IDs of the source and the target node for each edge. The following columns are edge attributes (weight, type, label, or anything else).

vertices starts with a column of node IDs. Any following columns are interpreted as node attributes.

```{r message = FALSE, warning= FALSE}
net <- graph_from_data_frame(d=links, vertices=nodes, directed=T) # Created data above

class(net)

net

# Think of it essentially like a neural network!

```

We also have easy access to nodes, edges, and their attributes with:

```{r message = FALSE, warning= FALSE}

E(net)       # The edges of the "net" object

V(net)       # The vertices of the "net" object

E(net)$type  # Edge attribute "type"

V(net)$media # Vertex attribute "media"

```

Now that we have our igraph network object, let’s make a first attempt to plot it.


```{r message = FALSE, warning= FALSE}

plot(net, edge.arrow.size=.4,vertex.label=NA)

```
That doesn’t look very good. Let’s start fixing things by removing the loops in the graph.


```{r message = FALSE, warning= FALSE}

net <- simplify(net, remove.multiple = F, remove.loops = T) 

```

You might notice that we could have used simplify to combine multiple edges by summing their weights with a command like simplify(net, edge.attr.comb=list(weight="sum","ignore")). The problem is that this would also combine multiple edge types (in our data: “hyperlinks” and “mentions”).

If you need them, you can extract an edge list or a matrix from igraph networks.

```{r message = FALSE, warning= FALSE}

as_edgelist(net, names=T)

as_adjacency_matrix(net, attr="weight")

```

Or data frames describing nodes and edges:



```{r message = FALSE, warning= FALSE}

as_data_frame(net, what="edges")

as_data_frame(net, what="vertices")

```

4.2 Dataset 2
As we have seen above, this time the edges of the network are in a matrix format. We can read those into a graph object using graph_from_incidence_matrix(). In igraph, bipartite networks have a node attribute called type that is FALSE (or 0) for vertices in one mode and TRUE (or 1) for those in the other mode.

```{r message = FALSE, warning= FALSE}

head(nodes2)

```


```{r message = FALSE, warning= FALSE}
head(links2)
```

To transform a one-mode network matrix into an igraph object, use instead graph_from_adjacency_matrix().

We can also easily generate bipartite projections for the two-mode network: (co-memberships are easy to calculate by multiplying the network matrix by its transposed matrix, or using igraph’s bipartite.projection() function).

```{r message = FALSE, warning= FALSE}
net2 <- graph_from_incidence_matrix(links2)

table(V(net2)$type)

net2.bp <- bipartite.projection(net2)

```

We can calculate the projections manually as well:

```{r message = FALSE, warning= FALSE}
as_incidence_matrix(net2)  %*% t(as_incidence_matrix(net2)) 

t(as_incidence_matrix(net2)) %*%   as_incidence_matrix(net2)

```

```{r message = FALSE, warning= FALSE}
plot(net2.bp$proj1, vertex.label.color="black", vertex.label.dist=1,

     vertex.size=7, vertex.label=nodes2$media[!is.na(nodes2$media.type)])

# So we have two different projections in one igraph object
```

```{r message = FALSE, warning= FALSE}
plot(net2.bp$proj2, vertex.label.color="black", vertex.label.dist=1,

     vertex.size=7, vertex.label=nodes2$media[ is.na(nodes2$media.type)])

```

We can set the node & edge options in two ways - the first one is to specify them in the plot() function, as we are doing below.

```{r message = FALSE, warning= FALSE}
# Plot with curved edges (edge.curved=.1) and reduce arrow size:

plot(net, edge.arrow.size=.4, edge.curved=.1)

```

```{r message = FALSE, warning= FALSE}
# Set edge color to gray, and the node color to orange. 

# Replace the vertex label with the node names stored in "media"

plot(net, edge.arrow.size=.2, edge.curved=0,

     vertex.color="orange", vertex.frame.color="#555555",

     vertex.label=V(net)$media, vertex.label.color="black",

     vertex.label.cex=.7) 

```

The second way to set attributes is to add them to the igraph object. Let’s say we want to color our network nodes based on type of media, and size them based on audience size (larger audience -> larger node). We will also change the width of the edges based on their weight.

```{r message = FALSE, warning= FALSE}
# Generate colors based on media type:

colrs <- c("gray50", "tomato", "gold")

V(net)$color <- colrs[V(net)$media.type]



# Set node size based on audience size:

V(net)$size <- V(net)$audience.size*0.7



# The labels are currently node IDs.

# Setting them to NA will render no labels:

V(net)$label.color <- "black"

V(net)$label <- NA



# Set edge width based on weight:

E(net)$width <- E(net)$weight/6



#change arrow size and edge color:

E(net)$arrow.size <- .2

E(net)$edge.color <- "gray80"



E(net)$width <- 1+E(net)$weight/12

```

We can also override the attributes explicitly in the plot:

```{r message = FALSE, warning= FALSE}
plot(net, edge.color="orange", vertex.color="gray50") 

```

It helps to add a legend explaining the meaning of the colors we used:

```{r message = FALSE, warning= FALSE}

plot(net) 

legend(x=-1.5, y=-1.1, c("Newspaper","Television", "Online News"), pch=21,

       col="#777777", pt.bg=colrs, pt.cex=2, cex=.8, bty="n", ncol=1)
```

5.2 Network layouts
Network layouts are simply algorithms that return coordinates for each node in a network.

For the purposes of exploring layouts, we will generate a slightly larger 80-node graph. We use the sample_pa() function which generates a simple graph starting from one node and adding more nodes and links based on a preset level of preferential attachment (Barabasi-Albert model).

```{r message = FALSE, warning= FALSE}
net.bg <- sample_pa(80) 

V(net.bg)$size <- 8

V(net.bg)$frame.color <- "white"

V(net.bg)$color <- "orange"

V(net.bg)$label <- "" 

E(net.bg)$arrow.mode <- 0

plot(net.bg)

```
You can set the layout in the plot function:

```{r message = FALSE, warning= FALSE}

plot(net.bg, layout=layout_randomly)

```

Or you can calculate the vertex coordinates in advance:

```{r message = FALSE, warning= FALSE}
l <- layout_in_circle(net.bg)

plot(net.bg, layout=l)

```

l is simply a matrix of x, y coordinates (N x 2) for the N nodes in the graph. You can easily generate your own:

```{r message = FALSE, warning= FALSE}
l <- cbind(1:vcount(net.bg), c(1, vcount(net.bg):2))

plot(net.bg, layout=l)

```

Force-directed layouts try to get a nice-looking graph where edges are similar in length and cross each other as little as possible. They simulate the graph as a physical system. Nodes are electrically charged particles that repulse each other when they get too close. The edges act as springs that attract connected nodes closer together. As a result, nodes are evenly distributed through the chart area, and the layout is intuitive in that nodes which share more connections are closer to each other. 

The disadvantage of these algorithms is that they are rather slow and therefore less often used in graphs larger than ~1000 vertices. You can set the “weight” parameter which increases the attraction forces among nodes connected by heavier edges.

```{r message = FALSE, warning= FALSE}
l <- layout_with_fr(net.bg)

plot(net.bg, layout=l)

```

You will notice that the layout is not deterministic - different runs will result in slightly different configurations. Saving the layout in l allows us to get the exact same result multiple times, which can be helpful if you want to plot the time evolution of a graph, or different relationships – and want nodes to stay in the same place in multiple plots.

```{r message = FALSE, warning= FALSE}
par(mfrow=c(2,2), mar=c(0,0,0,0))   # plot four figures - 2 rows, 2 columns

plot(net.bg, layout=layout_with_fr)

plot(net.bg, layout=layout_with_fr)

plot(net.bg, layout=l)

plot(net.bg, layout=l)

```

Improving Network Plots

Notice that our network plot is still not too helpful. We can identify the type and size of nodes, but cannot see much about the structure since the links we’re examining are so dense. One way to approach this is to see if we can sparsify the network, keeping only the most important ties and discarding the rest.

```{r message = FALSE, warning= FALSE}
hist(links$weight)

mean(links$weight)

sd(links$weight)

```

There are more sophisticated ways to extract the key edges, but for the purposes of this exercise we’ll only keep ones that have weight higher than the mean for the network. In igraph, we can delete edges using delete_edges(net, edges):

```{r message = FALSE, warning= FALSE}
cut.off <- mean(links$weight) 

net.sp <- delete_edges(net, E(net)[weight<cut.off])

plot(net.sp) 

```

Another way to think about this is to plot the two tie types (hyperlink & mention) separately

```{r message = FALSE, warning= FALSE}
E(net)$width <- 1.5

plot(net, edge.color=c("dark red", "slategrey")[(E(net)$type=="hyperlink")+1],

      vertex.color="gray40", layout=layout.circle)

```

```{r message = FALSE, warning= FALSE}
net.m <- net - E(net)[E(net)$type=="hyperlink"] # another way to delete edges

net.h <- net - E(net)[E(net)$type=="mention"]



# Plot the two links separately:

par(mfrow=c(1,2))

plot(net.h, vertex.color="orange", main="Tie: Hyperlink")

plot(net.m, vertex.color="lightsteelblue2", main="Tie: Mention")

```

5.4 Interactive plotting with tkplot
R and igraph allow for interactive plotting of networks. This might be a useful option for you if you want to tweak slightly the layout of a small graph. After adjusting the layout manually, you can get the coordinates of the nodes and use them for other plots.

```{r message = FALSE, warning= FALSE}
tkid <- tkplot(net) #tkid is the id of the tkplot that will open

l <- tkplot.getcoords(tkid) # grab the coordinates from tkplot

tk_close(tkid, window.close = T)

plot(net, layout=l)

# Didn't go interactive for me for some reason?

```

6. Network and node descriptives

6.1 Density
The proportion of present edges from all possible edges in the network.

```{r message = FALSE, warning= FALSE}

edge_density(net, loops=F)

```

```{r message = FALSE, warning= FALSE}
ecount(net)/(vcount(net)*(vcount(net)-1)) #for a directed network

```

6.2 Reciprocity
The proportion of reciprocated ties (for a directed network).

```{r message = FALSE, warning= FALSE}
reciprocity(net)

dyad_census(net) # Mutual, asymmetric, and nyll node pairs

2*dyad_census(net)$mut/ecount(net) # Calculating reciprocity

```

6.3 Transitivity
global - ratio of triangles (direction disregarded) to connected triples.
local - ratio of triangles to connected triples each vertex is part of.

```{r message = FALSE, warning= FALSE}
transitivity(net, type="global")  # net is treated as an undirected network

transitivity(as.undirected(net, mode="collapse")) # same as above

transitivity(net, type="local")

triad_census(net) # for directed networks 

```

6.4 Diameter
A network diameter is the longest geodesic distance (length of the shortest path between two nodes) in the network. In igraph, diameter() returns the distance, while get_diameter() returns the nodes along the first found path of that distance.

Note that edge weights are used by default, unless set to NA.

```{r message = FALSE, warning= FALSE}
diameter(net, directed=F, weights=NA)
diameter(net, directed=F)
diam <- get_diameter(net, directed=T)
diam

```

6.6 Degree distribution

```{r message = FALSE, warning= FALSE}
deg <- degree(net, mode="all")
deg.dist <- degree_distribution(net, cumulative=T, mode="all")

plot( x=0:max(deg), y=1-deg.dist, pch=19, cex=1.2, col="orange", 

      xlab="Degree", ylab="Cumulative Frequency")

```

6.7 Centrality & centralization

Centrality functions (vertex level) and centralization functions (graph level).

The centralization functions return res - vertex centrality, centralization, and theoretical_max - maximum centralization score for a graph of that size. 

Degree (number of ties)

```{r message = FALSE, warning= FALSE}
degree(net, mode="in")

centr_degree(net, mode="in", normalized=T)

```

Closeness (centrality based on distance to others in the graph)
Inverse of the node’s average geodesic distance to others in the network.

```{r message = FALSE, warning= FALSE}
closeness(net, mode="all", weights=NA) 

centr_clo(net, mode="all", normalized=T) 

```

Eigenvector (centrality proportional to the sum of connection centralities)
Values of the first eigenvector of the graph matrix.

```{r message = FALSE, warning= FALSE}
eigen_centrality(net, directed=T, weights=NA)

centr_eigen(net, directed=T, normalized=T) 

```
Betweenness (centrality based on a broker position connecting others)
Number of geodesics that pass through the node or the edge.

```{r message = FALSE, warning= FALSE}
betweenness(net, directed=T, weights=NA)

edge_betweenness(net, directed=T, weights=NA)

centr_betw(net, directed=T, normalized=T)

```

8. Subgroups and communities

Before we start, we will make our network undirected. There are several ways to do that conversion:
  - We can create an undirected link between any pair of connected nodes (mode="collapse")
  - Create undirected link for each directed one in the network, potentially ending up with a multiplex graph (mode="each")
  - Create undirected link for each symmetric link in the graph (mode="mutual").

In cases when we may have ties A -> B and B -> A ties collapsed into a single undirected link, we need to specify what to do with their edge attributes using the parameter ‘edge.attr.comb’ as we did earlier with simplify(). 

Here we have said that the ‘weight’ of the links should be summed, and all other edge attributes ignored and dropped.

```{r message = FALSE, warning= FALSE}
net.sym <- as.undirected(net, mode= "collapse",

                         edge.attr.comb=list(weight="sum", "ignore"))

```

8.1 Cliques
Find cliques (complete subgraphs of an undirected graph)

```{r message = FALSE, warning= FALSE}
cliques(net.sym) # list of cliques       

sapply(cliques(net.sym), length) # clique sizes

largest_cliques(net.sym) # cliques with max number of nodes

```

```{r message = FALSE, warning= FALSE}
vcol <- rep("grey80", vcount(net.sym))

vcol[unlist(largest_cliques(net.sym))] <- "gold"

plot(as.undirected(net.sym), vertex.label=V(net.sym)$name, vertex.color=vcol)

```

8.2 Community detection
A number of algorithms aim to detect groups that consist of densely connected nodes with fewer connections across groups.

Community detection based on edge betweenness (Newman-Girvan)

High-betweenness edges are removed sequentially (recalculating at each step) and the best partitioning of the network is selected.

```{r message = FALSE, warning= FALSE}
ceb <- cluster_edge_betweenness(net) 

dendPlot(ceb, mode="hclust")

```

```{r message = FALSE, warning= FALSE}

plot(ceb, net) 

# THIS FUNCTION IS VERY IMPORTANT!

```

Let’s examine the community detection igraph object:

```{r message = FALSE, warning= FALSE}
length(ceb)     # number of communities
membership(ceb) # community membership for each node
modularity(ceb) # how modular the graph partitioning is
crossing(ceb, net)   # boolean vector: TRUE for edges across communities

```

8.3 K-core decomposition

The k-core is the maximal subgraph in which every node has degree of at least k. The result here gives the coreness of each vertex in the network. A node has coreness D if it belongs to a D-core but not to (D+1)-core.

```{r message = FALSE, warning= FALSE}



```

```{r message = FALSE, warning= FALSE}



```

```{r message = FALSE, warning= FALSE}



```

```{r message = FALSE, warning= FALSE}



```

